Inspecting {glmnet} performances

### 2020-03-23 analysis/about.Rmd

José Cortés

@@

- What to do first (Feature selection or tuning): https://datascience.stackexchange.com/a/19778/24475
- Hastie, T., Friedman, J., & Tibshirani, R. (2001). The Elements of Statistical Learning. Springer New York. https://doi.org/10.1007/978-0-387-21606-5 (Kapitel 16)
- FSel algs overview: http://featureselection.asu.edu/algorithms.php
- De Jay, N., Papillon-Cavanagh, S., Olsen, C., El-Hachem, N., Bontempi, G., & Haibe-Kains, B. (2013). mRMRe: an R package for parallelized mRMR ensemble feature selection. Bioinformatics, 29(18), 2365–2368. https://doi.org/10/f48vxc
- Drotár, P., Gazda, J., & Smékal, Z. (2015). An experimental comparison of feature selection methods on two-class biomedical datasets. Computers in Biology and Medicine, 66, 1–10. https://doi.org/10/f72ttc
- Drotár, P., Šimoňák, S., Pietriková, E., Chovanec, M., Chovancová, E., Ádám, N., … Biňas, M. (2017). Comparison of Filter Techniques for Two-Step Feature Selection. COMPUTING AND INFORMATICS, 36(3), 597–617. https://doi.org/10/gbntp7
- Drotár, P., Gazda, M., & Gazda, J. (2017). Heterogeneous ensemble feature selection based on weighted Borda count. In 2017 9th International Conference on Information Technology and Electrical Engineering (ICITEE) (pp. 1–4). https://doi.org/10.1109/ICITEED.2017.8250495
- Nie, F., Huang, H., Cai, X., & Ding, C. H. (2010). Efficient and Robust Feature Selection via Joint \mathscrl2,1-Norms Minimization. In J. D. Lafferty, C. K. I. Williams, J. Shawe-Taylor, R. S. Zemel, & A. Culotta (Eds.), Advances in Neural Information Processing Systems 23 (pp. 1813–1821). Curran Associates, Inc. Retrieved from http://papers.nips.cc/paper/3988-efficient-and-robust-feature-selection-via-joint-l21-norms-minimization.pdf

>>>>

José Cortés [![](https://orcid.org/sites/default/files/images/orcid_16x16.png)](http://orcid.org/0000-0003-2567-8689)

@@

- What to do first (Feature selection or tuning): https://datascience.stackexchange.com/a/19778/24475
- {glmnet}: How to select lambda and alpha: https://stats.stackexchange.com/questions/357190/glmnet-how-to-select-lambda-and-alpha/415248#415248
- Hastie, T., Friedman, J., & Tibshirani, R. (2001). The Elements of Statistical Learning. Springer New York. https://doi.org/10.1007/978-0-387-21606-5 (Kapitel 16)
- FSel algs overview: http://featureselection.asu.edu/algorithms.php
- De Jay, N., Papillon-Cavanagh, S., Olsen, C., El-Hachem, N., Bontempi, G., & Haibe-Kains, B. (2013). mRMRe: an R package for parallelized mRMR ensemble feature selection. Bioinformatics, 29(18), 2365–2368. https://doi.org/10/f48vxc
- Drotár, P., Gazda, J., & Smékal, Z. (2015). An experimental comparison of feature selection methods on two-class biomedical datasets. Computers in Biology and Medicine, 66, 1–10. https://doi.org/10/f72ttc
- Drotár, P., Šimoňák, S., Pietriková, E., Chovanec, M., Chovancová, E., Ádám, N., … Biňas, M. (2017). Comparison of Filter Techniques for Two-Step Feature Selection. COMPUTING AND INFORMATICS, 36(3), 597–617. https://doi.org/10/gbntp7
- Drotár, P., Gazda, M., & Gazda, J. (2017). Heterogeneous ensemble feature selection based on weighted Borda count. In 2017 9th International Conference on Information Technology and Electrical Engineering (ICITEE) (pp. 1–4). https://doi.org/10.1109/ICITEED.2017.8250495
- Nie, F., Huang, H., Cai, X., & Ding, C. H. (2010). Efficient and Robust Feature Selection via Joint \mathscrl2,1-Norms Minimization. In J. D. Lafferty, C. K. I. Williams, J. Shawe-Taylor, R. S. Zemel, & A. Culotta (Eds.), Advances in Neural Information Processing Systems 23 (pp. 1813–1821). Curran Associates, Inc. Retrieved from http://papers.nips.cc/paper/3988-efficient-and-robust-feature-selection-via-joint-l21-norms-minimization.pdf

### 2020-03-23 analysis/inspect-glmnet-models.Rmd

# load drake objects
loadd(
  benchmark_models_new_penalized_mbo_buffer2,
  task_new_buffer2
)
```

@@

@@

>>>>

# load drake objects
loadd(
  benchmark_models_new_penalized_mbo_buffer2,
  task_new_buffer2,
  task_new_buffer2_reduced_cor
)
```

@@

```{r}
pred[which(pred > 100), , drop = FALSE]
```

@@

## Train/predict via {glmnet} manually on dataset with filtered feature correlation

obs_train_f4 <- as.matrix(task_new_buffer2_reduced_cor[[2]]$env$data[train_inds_fold4, getTaskFeatureNames(task_new_buffer2_reduced_cor[[2]])])
target_f4 <- getTaskTargets(task_new_buffer2_reduced_cor[[2]])[train_inds_fold4]
```

obs_pred_f4 <- as.matrix(task_new_buffer2_reduced_cor[[2]]$env$data[pred_inds_fold4, getTaskFeatureNames(task_new_buffer2_reduced_cor[[2]])])

```{r}
truth <- task_new_buffer2_reduced_cor[[2]]$env$data[pred_inds_fold4, "defoliation"]
